\chapter{Phrases tirées de VerbNet}
% Trouve un titre plus spécifique
%\begin{table}
\begin{longtable}{llr}
\caption{Phrases tirées de VerbNet pour effectuer l'évaluation}
%\begin{tabular}{llr}
 \toprule
 ID structure & Phrase\\
 \midrule
 17	&	I loved writing.	\\
27	&	They allow smoking.	\\
36	&	Plays and ballets alternate.	\\
77	&	I begged her to do it.	\\
111	&	The dragon breathed fire on Mary.	\\
142	&	Oils's price increased ten percent.	\\
177	&	The doctor cured Pat of pneumonia.	\\
198	&	She classified the works as 'dangerous'.	\\
206	&	Cora coiled the rope around the post.	\\
213	&	The prime minister complained to the former president about U.S. 
      interference in his country's affairs.	\\
222	&	The Milky Way comprises more than 100 billion planets.	\\
227	&	The children hid from Sally.	\\
244	&	They considered him professor.	\\
250	&	I spent the time on worries.	\\
264	&	Some of the members may donate privately.	\\
267	&	He converted to believing in Buddha.	\\
330	&	This flyer and that flyer differ.	\\
384	&	He entered the room.	\\
399	&	The bells traded places.	\\
426	&	We focused on it.	\\
428	&	We brooded about it.	\\
452	&	Carmen bought a dress for \$50.	\\
476	&	The teacher gathered the kids.	\\
503	&	Smith was inscribing.	\\
540	&	We abandoned the area.	\\
554	&	Sasha dawdled in the museum.	\\
581	&	I anguished over Aslan's pain.	\\
583	&	Dina masqueraded as a lawyer.	\\
604	&	Herman added a computer to the network.	\\
618	&	I neglected to do the job.	\\
630	&	She laughed in embarrassment.	\\
667	&	Lydia pocketed the change in her left pocket.	\\
686	&	Donna grilled me steaks.	\\
688	&	The dealer valued the book.	\\
746	&	Tom jumped the horse over the fence.	\\
750	&	The horse jumped the stream.	\\
777	&	TransCanada is shifting its HQ to Calgary from Toronto.	\\
789	&	The crew spotted the island.	\\
836	&	The thief stole the paint for Mary.	\\
843	&	I ended the party with a speech.	\\
845	&	Winnie the Pooh subjugated the unfortunate Pixies.	\\
851	&	The streets gushed with water.	\\
862	&	The sailor drowned.	\\
868	&	Bees are swarming in the garden.	\\
873	&	Paula swatted the fly with a cloth.	\\
894	&	Ellen told Helen a story.	\\
900	&	Steve tossed the ball from the corner to the garden.	\\
955	&	Linda winked her eye.	\\
968	&	Barry Cryer erased the writing.	\\
974	&	He backed out of going on the trip.	\\
 \midrule
%\end{tabular}
\end{longtable}
%\end{table}